Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?

### 2019-12-02 manuscript.Rmd

load("data/travel_times_census_join.RData")
load("data/dc_acs_tracts.RData")
theme_map <- theme_void()

travel_times <- travel_times %>%
	mutate(origin_id = factor(origin_id),
				 dest_id = factor(dest_id))

head(travel_times)

#primary_secondary_roads includes interstates and other highways in DC
dc_roads <- primary_secondary_roads(state="DC") %>%
	st_transform(crs = 102285)
```

```{r}

#tigris package - contains roads for DC
options(tigris_class="sf")
#primary_secondary_roads includes interstates and other highways in DC
dc_roads <- primary_secondary_roads(state= c("DC", "VA")) %>%
	st_transform(crs = 102285)
```

>>>>

load("data/travel_times_census_join.RData")
load("data/dc_acs_tracts.RData")
load("data/metro_lines.RData")
load("data/dc_roads.RData")
theme_map <- theme_void()
```
